Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-03-23 finalReportPres.tex
Update finalReportPres.tex

%==============================================================================
%     TITLE
%==============================================================================
\title[Smart Robotic Cart]{Smart Robotic Cart: A Prototype}

\author[K.~Allen, D.~Beebe, J.~Braker]{Kallistah~Allen \and Darrah~Beebe \and Jason~Braker
Advisors:~Dr.~Suruz~Miah \and Dr.~Prasad~Shastry}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\date[April~20,~2021]{Tuesday, April~27,~2021}

>>>>

%==============================================================================
%     TITLE
%==============================================================================
\title[HIL Plant Modeling]{Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle}

\author[H.~Grady, N.~Nauman]{Hannah~Grady \and Nicholas~Nauman 
\linebreak Advisor:~Dr.~Suruz~Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

@@

\date[April~29,~2022]{Tuesday, April~29,~2022}
